---
title: DANL Project
subtitle: "Data-Driven Mastery: Unlocking Business Potential"
author: 
  - Quinn Campbell
  - Andrew Johnson
  - Tristan Costello

toc: true
toc-title: "Table of Contents"
toc-depth: 2
number-sections: true

fig-width: 9

execute:
  code-tools: true
  message: false
  warning: false

from: markdown+emoji
---
```{r setup}
#| include: false
library(tidyverse)
library(skimr)
library(ggthemes)
library(hrbrthemes)

theme_set(theme_ipsum()+
          theme(strip.background =element_rect(fill="lightgray"),
                axis.title.x = 
                  element_text(angle = 0,
                               size = rel(1.33),
                               margin = margin(10,0,0,0)),
                axis.title.y = 
                  element_text(angle = 0,
                               size = rel(1.33),
                               margin = margin(0,10,0,0))
                )
          )
```



# Introduction

About This Project :clap:

```{r}
1 + 1
```


# Data

hoopR is an R package for working with men’s basketball data.

The package has functions to access live play by play and box score data from ESPN with shot locations when available. As of version 1.3.0, hoopR is also a full NBA Stats API wrapper with 127 functions added in this release.

It is additionally a scraping and aggregating interface for Ken Pomeroy’s men’s college basketball statistics website, kenpom.com. It provides users with an active subscription the capability to scrape the website tables and analyze the data for themselves.


## Summary Statistics

```{r}
mpg <- ggplot2::mpg
```

```{r}
#| results: asis
#| echo: false
rmarkdown::paged_table(mpg) 
```


```{r}
skim(mpg) %>% 
  select(-n_missing)
```


## MPG and a Type of Cars
The following boxplot shows how the distribution of highway MPG (`hwy`) varies by a type of cars (`class`) :blue_car: :truck: :minibus:.


```{r}
ggplot(data = mpg) +
  geom_boxplot(aes(x = class, y = hwy, fill = class),
               show.legend = F) +
  labs(x = "Class", y = "Highway\nMPG") 
```


